### 2013-10-31 NeurounitFrontiers/Paper.tex
Updated abstract

\section{Abstract}
Rigorously validating a scientific model's explanatory power requires comparing its predictions against empirical data on an ongoing basis. 
However, model validation remains an informal and incomplete process, especially in fields, like neuroscience, where the available data is growing rapidly.   
This makes it difficult to develop a contemporary understanding of a model's strengths and weaknesses, to adequately compare competing models to determine the state-of-the-art, and to precisely identify open modeling problems.

Software engineers validate software by developing simple executable tests, called ``unit tests'', that individually check a portion of a program against a single correctness criterion. Suites of such unit tests that collectively capture the desired program behavior provide evidence for its validity and correctness. Drawing inspiration from this practice, we develop the \textit{SciUnit} framework for developing suites of ``model validation tests'' -- 
executable functions, here written in Python, that compare model predictions against single empirical observations to  produce a score indicating agreement between the model and the data. Suites of such validation tests are used as a summary of modeling progress within a scientific community. 
Using this framework, we develop \textit{NeuroUnit}, a library that aids validation testing in neuroscience\todo{neurophys specifically?}.

>>>>

\section{Abstract}
Rigorously validating a scientific model's explanatory power requires comparing its predictions against empirical data on an ongoing basis. 
However, model validation remains an informal and incomplete process, especially in fields like neuroscience where the available data is growing rapidly.   
This makes it difficult to develop a contemporary understanding of a model's strengths and weaknesses, to adequately compare competing models, to determine the state-of-the-art, and to precisely identify open modeling problems.

Software engineers validate software by developing simple executable tests, called ``unit tests'', that individually check a portion of a program against a single correctness criterion. Suites of such unit tests that collectively capture the desired program behavior provide evidence for its validity and correctness. Drawing inspiration from this practice, we develop the \textit{SciUnit} framework for developing suites of ``model validation tests'' -- 
executable functions, here written in Python, that compare model predictions against single empirical observations to  produce a score indicating agreement between the model and the data. Suites of such validation tests are used as a summary of modeling progress within a scientific community. 
Building on this framework, we develop \textit{NeuronUnit}, a library that supports validation testing for neurophysiology\todo{is this accurate?}.
